---
title: " Black Prison Popluation In the U.S. (1990-2016):"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(areaplot)
library(stringr)
library(dplyr)
library(ggplot2)
library("plotly")
library("dplyr")
library("tidyr")
library("stringr")
library(maps)
library(tidyverse)
library(mapproj)
library(knitr)
source("../source/analysis.R")
```


## Introduction and Summary:
This report I have created uses the incarceration data to get specific 
information about the prison system in the United States. As we all know, even 
though Racism impacts all people of color in this country, Black Americans are
the ones that experience the most racism. For that reason, I decided to use this
data to help me understand the population of Black people in prison from different
years and times. I created a table "inc_data" and chose the columns I wanted
to help me learn about Black Americans in the system. From there I created other
tables to help me answer questions. After using the "inc_data" I have learned 
that the highest average for the Black Prison population for all years starting from
1990 and ending in 2016 was **`r highest_mean`** and the lowest average for all the years
was **`r lowest_mean`**. I have also learned that in 2016, the average Black Prisoners
was **`r mean_pop_2016`**. I chose to look at 2016 because it's the last year on my table.
I have also learned about the difference between the starting year 1990 and 
the ending year 2016 averages which was **`r change`**. The year 1990 has an average of
**`r mean_1990`** Black Prisoners.


## Time Trend Chart:

This chart is good for looking at the year that had the most Black people in the 
system as a whole, we can see by following the points on the chart that it's 2013
as it had over 25 Million Black people in the system (Prison, jail, etc). We can also 
see the change in the Black population over the years.
```{r trend, echo=FALSE, warning=FALSE, message=FALSE}
source("../source/analysis.R")
z
```

## Comparison Chart:
This chart shows us the difference in the regions in the country. By looking at it
we can see that the "Northeast" had the highest population of Black prisoners.
This chart helps us see the regions that had the highest Black Prisoner pop. and
the regions that had lower.

```{r comparison, echo=FALSE, warning=FALSE, message=FALSE}
source("../source/analysis.R")
x
```


## Map of California:
This map shows the prison population of Black Americans from different counties 
in California from the year 2015, the green color represents the N/A values. By 
looking at the map and the "Population" color section we can see which county 
had the highest prisoners.

```{r map, echo=FALSE, warning=FALSE, message=FALSE}
source("../source/analysis.R")
final_ca
```

